Proof nets for first-order additive linear logic

### 2019-04-22 7 - FSCD 2019 - Final/ALL1.tex
changed acknowledgements

We would like to thank the anonymous referees for their constructive feedback. Dominic would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group. Willem was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}.

>>>>

We would like to thank the anonymous referees for their constructive feedback. Dominic Hughes would like to thank his host, Wes Holliday, at the UC Berkeley Logic Group. Willem Heijltjes was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing}, and Lutz Stra{\ss}burger was supported by the ANR-FWF international
grant ANR-5-CE25-0014 \emph{The Fine Structure of Formal Proof
Systems and their Computational Interpretations (FISP)}.
